---
title: "Midterm 1"
author: "Enxhi Buxheli"
date: "3/7/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Attaching necessary libraries
# WARNING: when trying to use select, needed to specify dplyr::select
library(tidyverse)
library(mediation)
library(memisc)
library(Zelig)
library(gplots)
library(haven)
library(dplyr)

# Looking at the dataverse_files for the replication, anxiety.csv looks like
# it's use provided information while mTurk (assuming from Amazon Mechanical
# Turk) is the test output from the experiment [MAYBE]
```

```{r}
# age: age of the test subject
# storycond: indicator for which randomly assigned 1 of 2 stories for subject (Jose/Niko)
# relaxvid: indicator for whether or not subject saw relaxing video "Crystal Chakra"
# anxcond = anxietyvid: indicator for if subject saw anxiety video "Cliffhanger"
# anxcond3: indicator whether under relaxed (0), neutral (1), or anxiety (2) conditions 
# emo: emotion on which they gave the self-reported immigration rating
# immigration: response to 5-point scale on immigration statements (pg. 6)
# ideology: political preference with 1 - Liberal, 7 - Conservative
# CellId: 1-3 (Niko, RNA), 4-6 (Jose, RNA)
#
# anything with a vid suffix means that video stimulus was used 
#   [verifies that other emotions weren't inadvertently triggered]

# Reading in the STATA data file using a function from the haven library
# Looks like the numbers for age from STATA were forced to be integers (%8.0g)
data <- read_dta("dataverse_files/replicationdata.dta")

# Getting rid of the format attribute that says the data is from stata 
# This isn't necessary, but when looking at the data it won't show format
# anymore which is nice when handling. 
data <- zap_formats(data)

# The mean and sd for age check out!
mean(data$age, na.rm = TRUE)
sd(data$age, na.rm = TRUE)

### Data used for figure 2
## Skin conductivity during video
# Relaxed
filter(data, anxcond3 == 0) %>% 
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
# Neutral
filter(data, anxcond3 == 1) %>% 
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
# Anxiety
filter(data, anxcond3 == 2) %>% 
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
```


# Not necessary at the moment
*Label variables so tables look nice
label var SCDBradVidManipAll_mean "SCD (Mean) During Video"
label var SCDBradSelfReport1_mean "SCD (Mean) While Answering Questions"
label var emo "Self-Reported Immigration Beliefs"
label var CellID "Brader Condition (6 cells)"
label var anxcond "Anxiety Manipulation Dummy"
label var storycond "Story Condition"
label var interaction "Story X Anxiety"
label variable age "Age"
label variable race "Race"
label variable income "Income"
label variable education "Education"
label variable ideology "Ideology"
label variable anxietyvid "Anxiety Manipulation"
label variable relaxvid "Relax Manipulation"
label variable anxcond3 "Anxiety Condition"
label variable immigration "Immigration DV"





*Figure 2 
* Means of Skin Conductance Reactivity by Video Condition
ciplot SCDBradVidManipAll_mean,by(anxcond3)


* Table 1 in paper
* (1)
reg SCDBradSelfReport1_mean anxcond if anxcond3 ~=0

* (2) 
reg immigration storycond anxcond SCDBradSelfReport1_mean if anxcond3 ~=0



# Figure 3
```{r, results='asis'}
# Figure 3
# Causal Mediation Plot


# # Load Data
# anxiety <- read.csv("dataverse_files/anxiety.csv")
# 
# ## Make Subsets (do this last)
# noRelaxCond <- subset(anxiety, anxcond3 > 0)
# 
# # Outcome Model
# y <-
#   zelig(
#     immigration ~ anxcond + SCDBradSelfReport1_mean + storycond,
#     model = "ls",
#     data = noRelaxCond
#   )
# summary(y) # summarize results from model
# 
# # Mediator Model
# m <-
#   zelig(SCDBradSelfReport1_mean ~ anxcond + storycond,
#     model = "ls",
#     data = noRelaxCond
#   )
# summary(m) # summarize results from model
# 
# # Mediation Analysis
# m.out <-
#   mediate(
#     m,
#     y,
#     sims = 500,
#     treat = "anxcond",
#     mediator = "SCDBradSelfReport1_mean",
#     dropobs = TRUE,
#     boot = TRUE,
#     conf.level = .90
#   )
# summary(m.out)
# plot(
#   m.out,
#   labels = c(
#     "ACME\n(Physiological \nReactivity)",
#     "Direct Effect \n(Anxiety)",
#     "Total Effect"
#   )
# )
```

