---
title: "Midterm 1"
author: "Enxhi Buxheli"
date: "3/7/2019"
output: pdf_document
citation_package: natbib
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

# Attaching necessary libraries
# WARNING: when trying to use select, needed to specify dplyr::select
#   After eliminating some libraries as they were not necessary, this
#   may not be necessary anymore. Need to check.
library(tidyverse)
library(dplyr)
library(mediation)
library(haven)
library(ggplot2)
library(rstanarm)
library(rstan)
library(loo)
library(tibble)
library(stargazer)
library(knitr)

# Looking at the dataverse_files for the replication, anxiety.csv looks like
# it's use provided information while mTurk (assuming from Amazon Mechanical
# Turk) is the test output from the experiment [MAYBE]
```

# Abstract: 
Below is a replication of the tables and figures from J. Renshon, J. Lee, and D. Tingley's "Physiological Arousal and Political Beliefs" [@paper]. This replication draws from code taken from the Dataverse [@arousal] on the paper, but builds on it. The intention of this replication is to provide a better understanding and present the data and tables in a more appealing way. In addition to this, the code was remade using R rather than the original mixed use of Stata and R but also refines the existing code base for the existing paper. In the paper, there are three figures and one table. Figures 2 and 3 and Table 1 can be replicated completely, although I chose to make some modifications to their appearance and presentation. Figure 1 cannot be reproduced using R or any type of statistical or quantitative coding as it is diagram of the experiment's procedures. In the experiment, @arousal finds that physiological reactivity mediated the relationship between anxiety and political attitudes through treatment conditions. I also extended the modelling done in the paper by considering ideology as a factor in the immigration preferences, examining mediation effects, and also by performing Bayesian modelling rather than the simple linear modelling done in the paper. Even when including ideology, the result remained that physiological reactivity played a role in the mediation of effects. Additionally, ideology played a slight role in the determination of immigration preferences, but not of significance.

Really thorough and informative introduction!


```{r cleanup}
Great notes to include. Super helpful for you if you ever come back, and anyone replicating

# age: age of the test subject
# storycond: indicator for which randomly assigned 1 of 2 stories for subject (Jose/Niko)
# relaxvid: indicator for whether or not subject saw relaxing video "Crystal Chakra"
# anxcond = anxietyvid: indicator for if subject saw anxiety video "Cliffhanger".
#       This is also a binary on whether the person was given a stressful
#       scenario or not (neutral)
# anxcond3: indicator whether under relaxed (0), neutral (1), or anxiety (2) conditions 
# emo: emotion on which they gave the self-reported immigration rating
# immigration: response to 5-point scale on immigration statements (pg. 6)
# ideology: political preference with 1 - Liberal, 7 - Conservative
# CellId: 1-3 (Niko, Relax Neutral Anxiety), 4-6 (Jose, Relax Neutral Anxiety)
# SCDBradVidManipAll_mean: mean skin conductivity
#
# anything with a vid suffix means that video stimulus was used 
#   [verifies that other emotions weren't inadvertently triggered]

# Reading in the STATA data file using a function from the haven library
# Looks like the numbers for age from STATA were forced to be integers (%8.0g)
data <- read_dta("dataverse_files/replicationdata.dta") %>% 
  dplyr::select(anxcond, anxcond3, storycond, immigration, ideology,
                SCDBradSelfReport1_mean, SCDBradVidManipAll_mean)

# Getting rid of the format attribute that says the data is from stata 
# This isn't necessary, but when looking at the data it won't show format
# anymore which is nice when handling. Here I tried to recode the data to 
# make it easier to read, but ran into troubles when trying to group it.
# The data showed up fine, but the grouping failed...
data <- zap_formats(data) 

# The mean and sd for age check out!
# This output is not included in the output because it is not
# necessary for the replication. Just a sanity check.
# mean(data$age, na.rm = TRUE)
# sd(data$age, na.rm = TRUE)
```

# Replications:
## Figure 2
```{r fig2, results='asis'}
# Below you will find a lot of code in order to make the confidence 
# interval for figure 2. It was tedious, it was anxiety-inducing, but
# it eventually worked. For whatever reason, the confint function was 
# a bit finnicky and created strange outputs which forced me to use 
# the output that was coming out. Not quite sure if it was maybe because
# of updates to packages, a bug in the package, or a bug in my code, but 
# the output from my function to create a confidence interval just 
# didn't come out like I expected. I refined the code and made it as small
# as I could but there are some hackish ways that things were done. 
# Column names and row names were another thing that was just a bit more 
# touchy than I would've liked.

# Function to calculate the 95% confidence interval for Skin Conductivity based
# on the video treatment. This returns the lower and upper limit of the
# confidence interval for the linear model specificied in the paper.
anxiety_confint <- function(anxiety) {
  # Calculating confidence interval
  temp_dat <- filter(data, anxcond3 == anxiety)
  anx_SCDVid <- lm(SCDBradVidManipAll_mean ~ anxcond3, data = temp_dat)
  conf <- tibble(confint.lm(anx_SCDVid)[1,1:2])

  # Outputting the confidence interval
  conf
}

# Here are the confidence intervals properly formatted for output. These
# intervals were created using the anxiety_confint function above. Column
# names are changed for readability

# Relaxed with formatting
relax_conf   <- anxiety_confint("0") %>%
  mutate(treatment = "relax")
rownames(relax_conf) <- c("lower", "upper")
relax_conf <- rownames_to_column(relax_conf)
colnames(relax_conf) <- c("type", "interval", "treatment")
# Subsetting the data
low_relax <- filter(relax_conf, type == "lower")
up_relax  <- filter(relax_conf, type == "upper")

# Neutral with formatting
neutral_conf <- tibble(anxiety_confint("1")) %>%
  mutate(treatment = "neutral")
rownames(neutral_conf) <- c("lower", "upper")
neutral_conf <- rownames_to_column(neutral_conf)
colnames(neutral_conf) <- c("type", "interval", "treatment")
# Subsetting the data
low_neu <- filter(neutral_conf, type == "lower")
up_neu  <- filter(neutral_conf, type == "upper")

# Anxiety with formatting
anxiety_conf <- tibble(anxiety_confint("2")) %>%
  mutate(treatment = "anxiety")
rownames(anxiety_conf) <- c("lower", "upper")
anxiety_conf <- rownames_to_column(anxiety_conf)
colnames(anxiety_conf) <- c("type", "interval", "treatment")
# Subsetting the data
low_anx <- filter(anxiety_conf, type == "lower")
up_anx  <- filter(anxiety_conf, type == "upper")


# Creates a tibble of the lower and upper confidence intervals.
# The reason that it looks like such a mess is that the code didn't seem to run
# properly. For the first "relaxed" dataset, it gave the correct and expected
# output while for the rest it messed it up which caused me much anxiety and a
# lot of time was spent trying to resolve this but to no avail.
# Lower
lower_conf <- t(tibble(Relax = low_relax$interval,
                       Neutral = low_neu$interval$`confint.lm(anx_SCDVid)[1, 1:2]`,
                       Anxiety = low_anx$interval$`confint.lm(anx_SCDVid)[1, 1:2]`))
colnames(lower_conf) <- "lower"

# Upper
upper_conf <- t(tibble(Relax = up_relax$interval,
                       Neutral = up_neu$interval$`confint.lm(anx_SCDVid)[1, 1:2]`,
                       Anxiety = up_anx$interval$`confint.lm(anx_SCDVid)[1, 1:2]`))
colnames(upper_conf) <- "upper"

# Combining the data to be plotted
confidence <- cbind(lower_conf, upper_conf) 
means <- data %>% 
  filter(!is.na(anxcond3), !is.na(SCDBradVidManipAll_mean)) %>% 
  group_by(anxcond3) %>%
  summarise(mean = mean(SCDBradVidManipAll_mean)) %>% 
  arrange(anxcond3) 
         
# Binding the means and confidence to be plotted.
# This was a Eureka moment for me and made my code go from being defunct
# to being operational.
f2 <- cbind(means, confidence) %>% 
  rownames_to_column() 

### Data used for figure 2
## Skin conductivity during video
# Simple check for the data mean. 
# Relaxed mean
r_mean <- filter(data, anxcond3 == "0") %>%
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
# Neutral mean
n_mean <- filter(data, anxcond3 == "1") %>%
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
# Anxiety mean
a_mean <- filter(data, anxcond3 == "2") %>%
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))

# Plotting the data and making it look nice. Once I was able to 
# figure out how to get all of the data into one table that 
# ggplot could read, the graph was a breeze to make.
f2 %>% 
  ggplot() +
    geom_point(aes(x = rowname, y = mean)) + 
    geom_errorbar(aes(x = rowname, ymin = lower, ymax = upper,
                      color = "red"),
                      position = "dodge", width = 0.15,
                  show.legend = FALSE) +
    scale_y_continuous(limits = c(-0.5, 1.5)) +
    coord_flip() +
      labs(x = "Video Condition",
           y = "Skin Conductance Reactivity") +
    theme_light()
```
Good looking figure! I think have the "n= sample size" was one of the better aspects of their plot, so your plot would have been
perfect if you included those as well. It looks like you jumped through a lot of hoops to get the confidence interval for the different means. Certainly not a problem grading wise, you get the right answer, but a simple way would be to calculate the interval, and then add to the mean to get the upper bound, and subtract from the mean to get the lower bound. Or ci() from the gmodels package

m <- mean(var)
interval <- 1.96*sd(var)/sqrt(n)    where n is the number of observations 
low.bound <- m - interval
upper.bound <- m + interval

ci(var)

Figure 2: Means of skin-conductance reactivity by video condition. 95% confidence intervals are in red.

This plot shows mean skin conductivity when the subject was undergoing the video treatment. The confidence interval shows the range of skin conductivity for those of the different video treatments and see that an increase in anxiety is associated with an incresae in skin conductivity.

Excellent to have a description for what figure 2 is showing.

\newpage
## Table 1
```{r table1, results='asis'}
# Table 1 displays two linear regression models that comprise the two stages of
# a causal mediation model.

# According to the State code and the article, when they were running their
# regression they excluded the Relax condition as they wanted to see if Anxiety
# Manipulation was a factor in the skin conductivity and immigration preference
# rather than seeing the difference between the Relaxed, Neutral, and Anxiety
# conditions which wouldn't be good for trying to identify the specific effect
# of anxiety.

# Filter the data to only include the Neutral and Anxiety story conditions.
anx_data <- data %>%
  filter(anxcond3 != 0)

# Performing the linear regression for the filtered data based off of the
# specifications of the article and Stata code.
t1_anxiety <- lm(data = anx_data, SCDBradSelfReport1_mean ~ anxcond)
t1_imm     <- lm(data = anx_data, immigration ~ anxcond + storycond + SCDBradSelfReport1_mean)

stargazer(t1_anxiety, t1_imm,
          type = "latex",
          header = FALSE, style = "apsr", omit.stat = c("f","ser", "adj.rsq"), font.size = "small",
          column.sep.width = "-8pt", digits = 3,
          dep.var.labels = c("SC Reactivity", "Immigration Preference"),
          covariate.labels = c("Anxiety Manipulation","Story Condition",
                               "SC Reactivity while answering questions", "Constant"))
```
Note. Model (1) shows the effect of the treatment (anxiety) on physiological reactivity while Model (2) shows the effects of physiological reactivity on immigration preferences, controlling for the story condition. Both models includes only Neutral & Anxiety conditions (Relax condition is excluded).
Standard errors in brackets.

Perfect replication of Table 1. Maybe a bit more about why this table is important would be helpful to the reader.

\newpage
## Figure 3
```{r fig3, results='asis'}
# Figure 3
# Causal Mediation Plot

# The data I created [called data], and the anxiety data were the same bar the
# anxiety dataset having fewer fields. As a result, I used the overall data [my
# data] instead of loading in the anxiety.csv since they contain the same
# information, just not all of the same fields.

Perfectly acceptable choice.

# Outcome Model. This is the same as the immigration model from table 1. I
# created a new variable just to make the code more readable for this block.
outcome <- t1_imm
# summary(outcome)    # summarize results from model, used in development

# Mediator Model. This one I made into a lm function which already includes
# modelling as a default option. 
# Didn't know what a mediator was, so I took a look back at Gelman and Hill to
# find out that a mediator is a variable measured after the treatment has been
# done, but before the outcome of interest comes out. Here, our mediator looks
# at the skin conductivity relation resulting from anxiety and story conditions,
# but our outcome of interest is seeing the way which this impacts immigration
# preferences based on the treatment that they are given. The immigration
# preference outcome model takes into consideration skin conductivity while the
# mediator looks at the impact of skin conductivity based on teh anxiety and
# story condition which is also used in the outcome model.

Brief aside: Mediation analysis is attempting to see how much the effect of treatment (anxiety) is operating through the mediator (skin conductivity). So there is a direct effect (Anxiety -> Immigration Atts), but there is also an indirect effect (Anx -> Skin Cond. -> Immigration Atts). Mediation analysis tells if and how much of the effect of anxiety is operating through skin conductivity. So they show there is no direct effect of anxiety, which means that the skin conductivity from anxiety is actually what is resulting in changes, not just anxiety. It's generally accepted that emotion has an effect on political attitudes, but these authors want to show that it's not just changes in emotion, it's actually changes in emotion that result in a physiological response, and that it's this physical response that is causing attitude change.


mediator <- lm(data = anx_data, SCDBradSelfReport1_mean ~ anxcond + storycond)
# summary(mediator)    # summarize results from model, used in development

# Mediation Analysis
med_analysis <- mediate(mediator, outcome, sims = 500, treat = "anxcond",
                        mediator = "SCDBradSelfReport1_mean", 
                        dropobs = TRUE, boot = TRUE, conf.level = .90)
# summary(med_analysis)   # summarize results from model, used in development

# Here is the plot of the data in figure 3. I was trying to use other plotting
# libraries, but it seems that the mediation package only easily allows for the
# plotting of their mediate object with their own plot function. This plot
# function, while it doesn't seem to be, is a function of the package and can
# handle the mediate object.

# Setting the parameters for the plot output
par(family = "Times", cex = 0.75, mar = c(5,6,4,1)+.1)

## Notes on what the plot labels are.
# Average causal mediation effect (ACME) is the effect caused by the mediator
# Direct effect is the effect without considering the mediator
# Total efect is the combined effect of the mediator and the anxiety condition

# Plot output.
plot(med_analysis, labels = c("ACME\n(Physiological \nReactivity)", 
                              "Direct Effect \n(Anxiety)", 
                              "Total Effect"),
     main = "Linear Model of Treatment Effects with and without Mediation", xlab = "Magnitude of Effect")
```
Figure 3. Causal mediation plot. Treatment is anxiety video manipulation (compared to neutral condition), Mediator is skin conductance reactivity when answering immigration questions, Outcome is composite variable of immigration preferences. Horizontal lines represent 90% confidence intervals for estimates.

This plot is used to show that skin conductivity served as a mediator between anxiety and immigration preferences in treatment conditions. The direct effects are also quantified under "Immigration Preferences" in Table 1.

Really nice plot, excellent looking labels. Exactly what we were looking for.

# Extension: Bayesian Models and Comparisons
```{r ex1}
# Setting the seed for random number generation
set.seed(9)

# Creating a Bayesian model [and not showing all of the chains]
# adapt_delta reduces the likelihood for a biased model. Not absolutely
# sure what this means at a complex level, but I do know that biased models
# are bad and that this helps us avoid them.
hide1 <- capture.output(mod <- stan_glm(immigration ~ SCDBradSelfReport1_mean + storycond + anxcond,
                                       data = anx_data, control = list(adapt_delta = 0.99)))

# This second model will be used as a comparison to the model in the study to
# see if ideology plays a factor in the overall answer for immigration and
# if it provides a better fit overall.
hide2 <- capture.output(ideo_mod <- stan_glm(immigration ~ SCDBradSelfReport1_mean + storycond + anxcond + ideology,
                                             data = anx_data, control = list(adapt_delta = 0.99)))

# Variable with the Bayesian predictions
bayes_pred <- posterior_linpred(mod)

# View the predicted data in comparison to the actual immigration statistic.
# The following is used to see how well the Bayesian model predicts the actual
# data.
pp_check(mod, "dens_overlay") + 
  labs(title = "Immigration Preferences Distribution: Actual vs. Bayesian Linear Model Predictions",
       caption = "The Bayesian doesn't perform as well as it should because the bounds 
       of immgration preference weren't set to be between 1-5 for the model.") + 
  theme(plot.title = element_text(size = 12, face = "bold"))
cat("\n") 
pp_check(ideo_mod, "dens_overlay") +
  labs(title = "Immigration Preferences Distribution: Actual vs. Bayesian (Ideology Inclusive) Linear Model Predictions",
       caption = "This Bayesian has a larger tailing on the left,
       which is undesirable but the model fits well.") +
  theme(plot.title = element_text(size = 10, face = "bold"))
```

## Mediation Effects on Bayesian Model, Inclusive of Ideology
```{r ex2, results='asis'}
# Creating a new mediator that includes ideology as being a contributor to skin
# conductivity as posited by the original article pg.12

I think you may have meant to include ideology in the regression model below?

ideo_mediator <- lm(data = anx_data, SCDBradSelfReport1_mean ~ anxcond + storycond)

# Creating a mediation plot to see if the effects hold in the gaussian
hide3 <- capture.output(bayes_med <- mediate(ideo_mediator, ideo_mod, sims = 500, treat = "anxcond",
                                             mediator = "SCDBradSelfReport1_mean", 
                                             dropobs = TRUE, conf.level = .90)) 

# Setting the parameters for the plot output
par(family = "Times", cex = 0.75, mar = c(5,6,4,1)+.1) 
plot(bayes_med, labels = c("ACME\n(Physiological \nReactivity)", 
                           "Direct Effect \n(Anxiety \n & Ideology)", 
                           "Total Effect"),
     main = "Bayesian Model of Treatment Effects with and without Mediation", xlab = "Magnitude of Effect")
```

This is a cool extension and a nice visualization, but the reader has to look at this for a bit to figure out what's going on. What do you mean predicted data in comparison to the actual immigration statistic in your comments? I know what you mean, but anyone who has not taken this class may be lost. Especially because it's in your comments and not in the actual report. Anything that helps explain the meaning of a figure should not be left in comments. No one should be left guessing what a figure in your replication/paper means. Remember, these take up valuable space, so if you inlcude them, make sure you tell the reader exactly what they are meant to convey. 

Extension of Figure 3: This is a causal mediation plot for the Bayesian model of immigration preferences inclusive of ideological effects. The horizontal lines represent 90% confidence intervals for estimates. We see that the Direct Effects are lower as a result of the introduction of ideology as a factor on immigration preferences, but that the ACME (average causal mediation effect is largely unchanged). This plot still shows that physiological reactivity mediated the relationship between anxiety and political attitudes.

## Model Predictivity: With and Without Ideology
```{r ex3}
# Performing a comparison of the basic linear model to the Bayesian model to 
# find which perform better. The mediator was used in Figure 3 to create predictions
# and is also the same model used in Table 1 for immigration preferences.
loo_ideo <- loo(ideo_mod)
loo_orig <- loo(mod)

# The compare yields a result which says that the second model is better.
# Unsure if this is the result of overfitting.
fit <- tibble(compare(loo_orig, loo_ideo)) %>% 
  rownames_to_column() %>% 
  mutate(rowname = recode(rowname,
                          "1" = "Model Fit",
                          "2" = "Standard Error"))
colnames(fit) <- c("Stats", "Magnitude")

# Outputting table with results of model predictivity
fit %>% 
  mutate(Magnitude = round(Magnitude, 2)) %>% 
  kable(booktabs = TRUE)
```

Since the model fit is positive when doing a leave-one-out comparison on the original paper's model to a new model where ideology is considered in immigration preferences, this means that the model which considers ideology is a better predictor of immigration preferences than the original paper. 

Why is the model fit better? Where did leave one out come from? What is magnitude? What does this have to do with predictivity? These are all questions that someone who reads this report might be asking and should be addressed in the report itself.

Overall, great job!


\newpage
# References
