---
title: "Midterm 1"
author: "Enxhi Buxheli"
date: "3/7/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

# Attaching necessary libraries
# WARNING: when trying to use select, needed to specify dplyr::select
#   After eliminating some libraries as they were not necessary, this
#   may not be necessary anymore. Need to check.
library(tidyverse)
library(dplyr)
library(mediation)
library(haven)
library(ggplot2)
library(rstanarm)
library(tibble)
library(stargazer)

# Looking at the dataverse_files for the replication, anxiety.csv looks like
# it's use provided information while mTurk (assuming from Amazon Mechanical
# Turk) is the test output from the experiment [MAYBE]
```

```{r cleanup}
# age: age of the test subject
# storycond: indicator for which randomly assigned 1 of 2 stories for subject (Jose/Niko)
# relaxvid: indicator for whether or not subject saw relaxing video "Crystal Chakra"
# anxcond = anxietyvid: indicator for if subject saw anxiety video "Cliffhanger".
#       This is also a binary on whether the person was given a stressful
#       scenario or not (neutral)
# anxcond3: indicator whether under relaxed (0), neutral (1), or anxiety (2) conditions 
# emo: emotion on which they gave the self-reported immigration rating
# immigration: response to 5-point scale on immigration statements (pg. 6)
# ideology: political preference with 1 - Liberal, 7 - Conservative
# CellId: 1-3 (Niko, Relax Neutral Anxiety), 4-6 (Jose, Relax Neutral Anxiety)
# SCDBradVidManipAll_mean: mean skin conductivity
#
# anything with a vid suffix means that video stimulus was used 
#   [verifies that other emotions weren't inadvertently triggered]

# Reading in the STATA data file using a function from the haven library
# Looks like the numbers for age from STATA were forced to be integers (%8.0g)
data <- read_dta("dataverse_files/replicationdata.dta")

# Getting rid of the format attribute that says the data is from stata 
# This isn't necessary, but when looking at the data it won't show format
# anymore which is nice when handling. Here I tried to recode the data to 
# make it easier to read, but ran into troubles when trying to group it.
# The data showed up fine, but the grouping failed...
data <- zap_formats(data) 

# The mean and sd for age check out!
# This output is not included in the output because it is not
# necessary for the replication. Just a sanity check.
# mean(data$age, na.rm = TRUE)
# sd(data$age, na.rm = TRUE)
```

# Figure 2
```{r figure2, results='asis'}
# Below you will find a lot of code in order to make the confidence 
# interval for figure 2. It was tedious, it was anxiety-inducing, but
# it eventually worked. For whatever reason, the confint function was 
# a bit finnicky and created strange outputs which forced me to use 
# the output that was coming out. Not quite sure if it was maybe because
# of updates to packages, a bug in the package, or a bug in my code, but 
# the output from my function to create a confidence interval just 
# didn't come out like I expected. I refined the code and made it as small
# as I could but there are some hackish ways that things were done. 
# Column names and row names were another thing that was just a bit more 
# touchy than I would've liked.

# Function to calculate the 95% confidence interval for Skin Conductivity based
# on the video treatment. This returns the lower and upper limit of the
# confidence interval for the linear model specificied in the paper.
anxiety_confint <- function(anxiety) {
  # Calculating confidence interval
  temp_dat <- filter(data, anxcond3 == anxiety)
  anx_SCDVid <- lm(SCDBradVidManipAll_mean ~ anxcond3, data = temp_dat)
  conf <- tibble(confint.lm(anx_SCDVid)[1,1:2])

  # Outputting the confidence interval
  conf
}

# Here are the confidence intervals properly formatted for output. These
# intervals were created using the anxiety_confint function above. Column
# names are changed for readability

# Relaxed with formatting
relax_conf   <- anxiety_confint("0") %>%
  mutate(treatment = "relax")
rownames(relax_conf) <- c("lower", "upper")
relax_conf <- rownames_to_column(relax_conf)
colnames(relax_conf) <- c("type", "interval", "treatment")
# Subsetting the data
low_relax <- filter(relax_conf, type == "lower")
up_relax  <- filter(relax_conf, type == "upper")

# Neutral with formatting
neutral_conf <- tibble(anxiety_confint("1")) %>%
  mutate(treatment = "neutral")
rownames(neutral_conf) <- c("lower", "upper")
neutral_conf <- rownames_to_column(neutral_conf)
colnames(neutral_conf) <- c("type", "interval", "treatment")
# Subsetting the data
low_neu <- filter(neutral_conf, type == "lower")
up_neu  <- filter(neutral_conf, type == "upper")

# Anxiety with formatting
anxiety_conf <- tibble(anxiety_confint("2")) %>%
  mutate(treatment = "anxiety")
rownames(anxiety_conf) <- c("lower", "upper")
anxiety_conf <- rownames_to_column(anxiety_conf)
colnames(anxiety_conf) <- c("type", "interval", "treatment")
# Subsetting the data
low_anx <- filter(anxiety_conf, type == "lower")
up_anx  <- filter(anxiety_conf, type == "upper")


# Creates a tibble of the lower and upper confidence intervals.
# The reason that it looks like such a mess is that the code didn't seem to run
# properly. For the first "relaxed" dataset, it gave the correct and expected
# output while for the rest it messed it up which caused me much anxiety and a
# lot of time was spent trying to resolve this but to no avail.
# Lower
lower_conf <- t(tibble(Relax = low_relax$interval,
                       Neutral = low_neu$interval$`confint.lm(anx_SCDVid)[1, 1:2]`,
                       Anxiety = low_anx$interval$`confint.lm(anx_SCDVid)[1, 1:2]`))
colnames(lower_conf) <- "lower"

# Upper
upper_conf <- t(tibble(Relax = up_relax$interval,
                       Neutral = up_neu$interval$`confint.lm(anx_SCDVid)[1, 1:2]`,
                       Anxiety = up_anx$interval$`confint.lm(anx_SCDVid)[1, 1:2]`))
colnames(upper_conf) <- "upper"

# Combining the data to be plotted
confidence <- cbind(lower_conf, upper_conf) 
means <- data %>% 
  filter(!is.na(anxcond3), !is.na(SCDBradVidManipAll_mean)) %>% 
  group_by(anxcond3) %>%
  summarise(mean = mean(SCDBradVidManipAll_mean)) %>% 
  arrange(anxcond3) 
         
# Binding the means and confidence to be plotted.
# This was a Eureka moment for me and made my code go from being defunct
# to being operational.
f2 <- cbind(means, confidence) %>% 
  rownames_to_column() 

### Data used for figure 2
## Skin conductivity during video
# Simple check for the data mean. 
# Relaxed mean
r_mean <- filter(data, anxcond3 == "0") %>%
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
# Neutral mean
n_mean <- filter(data, anxcond3 == "1") %>%
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))
# Anxiety mean
a_mean <- filter(data, anxcond3 == "2") %>%
  summarise(mean = mean(SCDBradVidManipAll_mean, na.rm = TRUE))

# Plotting the data and making it look nice. Once I was able to 
# figure out how to get all of the data into one table that 
# ggplot could read, the graph was a breeze to make.
f2 %>% 
  ggplot() +
    geom_point(aes(x = rowname, y = mean)) + 
    geom_errorbar(aes(x = rowname, ymin = lower, ymax = upper,
                      color = "red"),
                      position = "dodge", width = 0.15,
                  show.legend = FALSE) +
    scale_y_continuous(limits = c(-0.5, 1.5)) +
    coord_flip() +
      labs(x = "Video Condition",
           y = "Skin Conductance Reactivity") +
    theme_light()
```
Figure 2: Means of skin-conductance reactivity by video condition. 95% confidence intervals are in red.

# Table 1
```{r table1, results='asis'}
# Table 1 displays two linear regression models that comprise the two stages of
# a causal mediation model.

# According to the State code and the article, when they were running their
# regression they excluded the Relax condition as they wanted to see if Anxiety
# Manipulation was a factor in the skin conductivity and immigration preference
# rather than seeing the difference between the Relaxed, Neutral, and Anxiety
# conditions which wouldn't be good for trying to identify the specific effect
# of anxiety.

# Filter the data to only include the Neutral and Anxiety story conditions.
anx_data <- data %>%
  filter(anxcond3 != 0)

# Performing the linear regression for the filtered data based off of the
# specifications of the article and Stata code.
t1_anxiety <- lm(data = anx_data, SCDBradSelfReport1_mean ~ anxcond)
t1_imm     <- lm(data = anx_data, immigration ~ anxcond + storycond + SCDBradSelfReport1_mean)

stargazer(t1_anxiety, t1_imm,
          type = "latex",
          header = FALSE, style = "apsr", omit.stat = c("f","ser", "adj.rsq"), font.size = "small",
          column.sep.width = "-8pt", digits = 3,
          dep.var.labels = c("SC Reactivity", "Immigration Preference"),
          covariate.labels = c("Anxiety Manipulation","Story Condition",
                               "SC Reactivity while answering questions", "Constant"))
```



# Not necessary at the moment
*Label variables so tables look nice
label var SCDBradVidManipAll_mean "SCD (Mean) During Video"
label var SCDBradSelfReport1_mean "SCD (Mean) While Answering Questions"
label var emo "Self-Reported Immigration Beliefs"
label var CellID "Brader Condition (6 cells)"
label var anxcond "Anxiety Manipulation Dummy"
label var storycond "Story Condition"
label var interaction "Story X Anxiety"
label variable age "Age"
label variable race "Race"
label variable income "Income"
label variable education "Education"
label variable ideology "Ideology"
label variable anxietyvid "Anxiety Manipulation"
label variable relaxvid "Relax Manipulation"
label variable anxcond3 "Anxiety Condition"
label variable immigration "Immigration DV"

# Figure 3
```{r, results='asis'}
# Figure 3
# Causal Mediation Plot

# There is a slight difference between the data I created [and called data], and
# the anxiety data. Could potentially use the overall data [my data] instead of
# loading in the anxiety.csv since they contain the same information, just not
# all of the same fields.

# Loading in the anxiety data to be used in the creation of the Figure 3 plot.
anxiety <- read_csv("dataverse_files/anxiety.csv")

# This filters those that were under the neutral and anxiety
# conditions for the video condition similar to table 1. 
noRelaxCond <- anxiety %>% 
  filter(anxcond3 != 0)

# Outcome Model. This is the same model as from table 1.
y <- lm(data = noRelaxCond, immigration ~ anxcond + storycond + SCDBradSelfReport1_mean)
summary(y) # summarize results from model

# Mediator Model. This one I made into a lm function which
# already includes modelling as a default option.
m <- lm(data = noRelaxCond, SCDBradSelfReport1_mean ~ anxcond + storycond)
summary(m) # summarize results from model

# Mediation Analysis
m.out <- mediate(m, y, sims = 500, treat = "anxcond",
                 mediator = "SCDBradSelfReport1_mean", 
                 dropobs = TRUE, boot = TRUE, conf.level = .90)
summary(m.out)


plot(
  m.out,
  labels = c(
    "ACME\n(Physiological \nReactivity)",
    "Direct Effect \n(Anxiety)",
    "Total Effect"
  )
)
```

